Finding Maximum $k$-Cliques Faster \\ Using Lazy Global Domination

### 2016-07-01 talk/talk.tex
More talk

\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{vertexc1/.style={vertex, fill=uofgburgundy, text=white}}
\tikzset{vertexc2/.style={vertex, fill=uofgsandstone, text=white}}
\tikzset{vertexc3/.style={vertex, fill=uofgforest, text=white}}
\tikzset{vertexc4/.style={vertex, fill=uofgheather, text=white}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}

@@

\begin{frame}{Maximum Clique}
\end{frame}

\begin{frame}{Maximum $k$-Clique}
\end{frame}

\begin{frame}{Maximum $k$-Club}
\end{frame}

@@

\begin{frame}{Reducing $k$-Clique to Clique}
\end{frame}

@@

\begin{frame}{But We Can Do Better}
\end{frame}

>>>>

\tikzset{vertex/.style={draw, circle, inner sep=3pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{selectedvertex/.style={vertex, fill=uofgcobalt}}
\tikzset{selectedvertex2/.style={vertex, fill=uofglawn}}
\tikzset{redvertex/.style={vertex, fill=uofgpillarbox}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}

@@

\begin{frame}{Maximum Clique}
    \centering
    \begin{tikzpicture}
        \newcount \c
        \foreach \n in {1, ..., 8}{
            \c=\n \advance\c by -1 \multiply\c by -360 \divide\c by 8 \advance\c by 90 \advance\c by 22.5
            \ifthenelse{\n = 1 \OR \n = 2 \OR \n = 5 \OR \n = 8}{
                \node[selectedvertex] (N\n) at (\the\c:2) {\n};
            }{
                \node[plainvertex] (N\n) at (\the\c:2) {\n};
            }
        }

        \draw [edge] (N2) -- (N3);
        \draw [edge] (N2) -- (N4);
        \draw [edge] (N3) -- (N7);
        \draw [edge] (N4) -- (N5);
        \draw [edge] (N5) -- (N6);
        \draw [edge] (N6) -- (N7);

        \draw [bedge] (N1) -- (N2);
        \draw [bedge] (N1) -- (N5);
        \draw [bedge] (N1) -- (N8);
        \draw [bedge] (N2) -- (N5);
        \draw [bedge] (N2) -- (N8);
        \draw [bedge] (N5) -- (N8);
    \end{tikzpicture}
\end{frame}

\begin{frame}{Maximum $k$-Clique}
    \centering
    \begin{tikzpicture}
        \newcount \c
        \foreach \n in {1, ..., 8}{
            \c=\n \advance\c by -1 \multiply\c by -360 \divide\c by 8 \advance\c by 90 \advance\c by 22.5
            \ifthenelse{\n = 1 \OR \n = 2 \OR \n = 3 \OR \n = 4 \OR \n = 5 \OR \n = 6 \OR \n = 8}{
                \node[selectedvertex] (N\n) at (\the\c:2) {\n};
            }{
                \node[plainvertex] (N\n) at (\the\c:2) {\n};
            }
        }

        \draw [edge] (N3) -- (N7);
        \draw [edge] (N6) -- (N7);

        \draw [bedge] (N1) -- (N2);
        \draw [bedge] (N1) -- (N5);
        \draw [bedge] (N1) -- (N8);
        \draw [bedge] (N2) -- (N5);
        \draw [bedge] (N2) -- (N8);
        \draw [bedge] (N5) -- (N8);
        \draw [bedge] (N2) -- (N3);
        \draw [bedge] (N2) -- (N4);
        \draw [bedge] (N4) -- (N5);
        \draw [bedge] (N5) -- (N6);
    \end{tikzpicture}
\end{frame}

\begin{frame}{Maximum $k$-Club}
    \centering
    \begin{tikzpicture}
        \newcount \c
        \foreach \n in {1, ..., 8}{
            \c=\n \advance\c by -1 \multiply\c by -360 \divide\c by 8 \advance\c by 90 \advance\c by 22.5
            \ifthenelse{\n = 1 \OR \n = 2 \OR \n = 4 \OR \n = 5 \OR \n = 8}{
                \node[selectedvertex] (N\n) at (\the\c:2) {\n};
            }{
                \ifthenelse{\n = 3 \OR \n = 6}{
                    \node[redvertex] (N\n) at (\the\c:2) {\n};
                }{
                    \node[plainvertex] (N\n) at (\the\c:2) {\n};
                }
            }
        }

        \draw [edge] (N3) -- (N7);
        \draw [edge] (N6) -- (N7);

        \draw [bedge] (N1) -- (N2);
        \draw [bedge] (N1) -- (N5);
        \draw [bedge] (N1) -- (N8);
        \draw [bedge] (N2) -- (N5);
        \draw [bedge] (N2) -- (N8);
        \draw [bedge] (N5) -- (N8);
        \draw [bedge] (N2) -- (N3);
        \draw [bedge] (N2) -- (N4);
        \draw [bedge] (N4) -- (N5);
        \draw [bedge] (N5) -- (N6);
    \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Reducing $k$-Clique to Clique}
    \centering
    \begin{tikzpicture}
        \begin{scope}
            \newcount \c
            \foreach \n in {1, ..., 8}{
                \c=\n \advance\c by -1 \multiply\c by -360 \divide\c by 8 \advance\c by 90 \advance\c by 22.5
                \ifthenelse{\n = 1 \OR \n = 2 \OR \n = 3 \OR \n = 4 \OR \n = 5 \OR \n = 6 \OR \n = 8}{
                    \node[selectedvertex] (N\n) at (\the\c:2) {\n};
                }{
                    \node[plainvertex] (N\n) at (\the\c:2) {\n};
                }
            }

            \draw [edge] (N3) -- (N7);
            \draw [edge] (N6) -- (N7);

            \draw [bedge] (N1) -- (N2);
            \draw [bedge] (N1) -- (N5);
            \draw [bedge] (N1) -- (N8);
            \draw [bedge] (N2) -- (N5);
            \draw [bedge] (N2) -- (N8);
            \draw [bedge] (N5) -- (N8);
            \draw [bedge] (N2) -- (N3);
            \draw [bedge] (N2) -- (N4);
            \draw [bedge] (N4) -- (N5);
            \draw [bedge] (N5) -- (N6);
        \end{scope}
        \begin{scope}[xshift=6cm]
            \newcount \c
            \foreach \n in {1, ..., 8}{
                \c=\n \advance\c by -1 \multiply\c by -360 \divide\c by 8 \advance\c by 90 \advance\c by 22.5
                \ifthenelse{\n = 1 \OR \n = 2 \OR \n = 3 \OR \n = 4 \OR \n = 5 \OR \n = 6 \OR \n = 8}{
                    \node[selectedvertex] (N\n) at (\the\c:2) {\n};
                }{
                    \node[plainvertex] (N\n) at (\the\c:2) {\n};
                }
            }

            \draw [edge] (N2) -- (N7);
            \draw [edge] (N3) -- (N7);
            \draw [edge] (N5) -- (N7);
            \draw [edge] (N6) -- (N7);

            \draw [bedge] (N1) -- (N2);
            \draw [bedge] (N1) -- (N3);
            \draw [bedge] (N1) -- (N4);
            \draw [bedge] (N1) -- (N5);
            \draw [bedge] (N1) -- (N6);
            \draw [bedge] (N1) -- (N8);
            \draw [bedge] (N2) -- (N3);
            \draw [bedge] (N2) -- (N4);
            \draw [bedge] (N2) -- (N5);
            \draw [bedge] (N2) -- (N6);
            \draw [bedge] (N2) -- (N8);
            \draw [bedge] (N3) -- (N4);
            \draw [bedge] (N3) -- (N5);
            \draw [bedge] (N3) -- (N6);
            \draw [bedge] (N3) -- (N8);
            \draw [bedge] (N4) -- (N5);
            \draw [bedge] (N4) -- (N6);
            \draw [bedge] (N4) -- (N8);
            \draw [bedge] (N5) -- (N6);
            \draw [bedge] (N5) -- (N8);
            \draw [bedge] (N6) -- (N8);
        \end{scope}
    \end{tikzpicture}
\end{frame}

@@

\begin{frame}{But We Can Do Better}
    \centering
    \begin{tikzpicture}
        \begin{scope}
            \node[selectedvertex] (Na) at (0, 2) {$a$};
            \node[selectedvertex2] (Nb) at (6, 2) {$b$};

            \node[plainvertex] (N1) at (3, 4) {$1$};
            \node[plainvertex] (N2) at (3, 3) {$2$};
            \node[plainvertex] (N3) at (3, 2) {$3$};
            \node[plainvertex] (N4) at (3, 1) {$4$};
            \node[plainvertex] (N5) at (3, 0) {$5$};

            \draw [edge] (Na) -- (N1);
            \draw [edge] (Na) -- (N2);
            \draw [edge] (Na) -- (N3);
            \draw [edge] (Na) -- (N4);
            \draw [edge] (Na) -- (N5);

            \draw [edge] (Nb) -- (N1);
            \draw [edge] (Nb) -- (N3);
            \draw [edge] (Nb) -- (N5);
        \end{scope}
    \end{tikzpicture}
\end{frame}
